### 2015-03-26 SBACSystems.tex
SBAC + Biblio

Given a \texttt{Permission} object \texttt{p}, \texttt{p}'s
fully-qualified \texttt{Permission} class name along with
\texttt{p}'s target and action, if any, uniquely identify the
authorization requirement represented by \texttt{p}. Therefore,
for authorization purposes, a \texttt{Permission} object \texttt{p}
can be characterized solely based on its \textit{permission
	ID}, which consists of \textt{p}'s fully-qualified class name and
the values of the \texttt{String} instances used to instantiate
\texttt{p}.  In fact, in the Java Runtime Environment (JRE)
reference implementation, authorizations are granted to programs
and principals by just listing the corresponding permission IDs in
a flat-file policy database, called the \emph{policy file}
\cite{book:J2SESecBook}.

>>>>

Given a \texttt{Permission} object \texttt{p}, \texttt{p}'s
fully-qualified \texttt{Permission} class name along with
\texttt{p}'s target and action, if any, uniquely identify the
authorization requirement represented by \texttt{p}. Therefore,
for authorization purposes, a \texttt{Permission} object \texttt{p}
can be characterized solely based on its \textit{permission
	ID}, which consists of \texttt{p}'s fully-qualified class name and
the values of the \texttt{String} instances used to instantiate
\texttt{p}.  In fact, in the Java Runtime Environment (JRE)
reference implementation, authorizations are granted to programs
and principals by just listing the corresponding permission IDs in
a flat-file policy database, called the \emph{policy file}
\cite{book:J2SESecBook}.
